Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia

### 2024-02-11 outputs/paper/paper.qmd
create one more figure to the paper

# Results
## Figure 1 (Originally figure 2)

## Table 1 (Originally table 1)
```{r}
#| message: false
#| echo: false
# Read the dataset
main_clean <- read_dta(here("inputs/data/01_main_exp_clean_original.dta"))
follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean_original.dta"))
online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean_original.dta"))
```

>>>>

# Results
```{r}
#| message: false
#| echo: false
# Read the dataset
main_clean <- read_dta(here("inputs/data/01_main_exp_clean_original.dta"))
follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean_original.dta"))
online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean_original.dta"))
```

## Figure 1 (Originally figure 2)

## Figure 2 (Originally figure 3)
```{r}
#| message: false
#| echo: false
p_value_figure3 <- chisq.test(table(main_clean$condition2, main_clean$signed_up_number))

percentage_data_figure3 <- main_clean |>
  mutate(condition2 = ifelse(condition2 == 0, 'Control', 'Treatment')) |>
  group_by(condition2) |>
  summarise(percentage = mean(signed_up_number == 1) * 100)
```

```{r}
#| message: false
#| echo: false
#| label: fig-job_sign_up
#| fig-cap: Job Matching Service Sign Up (Main Experiment)
plot_figure3 <- ggplot(percentage_data_figure3, aes(x = condition2, y = percentage)) +
  geom_bar(stat = "identity", fill = "grey", color = "black", alpha = 0.9) +
  labs(x = "",
       y = "Percent sign up") +
  geom_text(aes(label = paste0(round(percentage, 2), "%")),
            position = position_dodge(width = 0.9),
            vjust = -0.5) +
  annotate("text", x = 1.5, y = 37, label = sprintf("p-value = %.4f", p_value_figure3$p.value)) +
  theme_minimal() + 
  ylim(0, 40)

plot_figure3
```

## Table 1 (Originally table 1)
